---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simboil

<!-- badges: start -->
<!-- badges: end -->

The goal of simboil is to stream line simulation workflows.  It hopes to bring simmering simmering simmering simulations to a boil.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mncube/simboil")
```
## Use Monte Carlo simulation to test a condition

The default setting of simtest simulates a coin flip and tests whether 10 flips
has 3 or more head (where head is defined as 1).  The function and example was 
inspired by A Beginner's Guide to Monte Carlo Simulations presented by Dan Uehara 
for UseR Oslo: https://www.youtube.com/watch?v=g2Uu9m0IlFE
```{r example}
library(simboil)
coinflips <- simtest()
mean(coinflips)
```

## Use simulation to get quantiles

In the example below, simq is used to compare a practice test to the test mean
and standard deviation from the past 3 years

```{r}
#Test scores from the new test administered over the past 3 years is not 
#available but the mean (75) and sd (14) is known
sim_scores <- as.vector(rnorm(1000, 75, 14))

#Practice test scores for low performing math class 
practice_test <- as.vector(rnorm(30, 68, 7))

#See how low performers compare to past performers

#Run simulation
getqs <- simq(frame = sim_scores, ref_samp = practice_test, 
              main = "Distribution of Past Tests", xlab = "Sample Means")

#Get requested quantiles (example uses defaults of lowp = .025, highp = .975)
getqs$quantiles

#Compare practice test to distribution of past tests
getqs$histogram
```

## Compare the empirical cdf to the true cdf using the plots

Plot the empirical vs true cdf for the uniform distribution as follows:
```{r}
evt_cdf(ylab = "Cumulative Probability", col = "blue", main = "Uniform ECDF (black) vs Uniform CDF (blue)")
```

To get a more accurate ECDF plot, increase the number of samples using n
```{r}
evt_cdf(n = 10^5, ylab = "Cumulative Probability", col = "blue", main = "Uniform ECDF (black) vs Uniform CDF (blue)")
```

You can also change from the uniform distribution to other distributions such as the normal distribution by using anonymous functions
```{r}
evt_cdf(n = 500, ylab = "Cumulative Probability", col = "blue", main = "Normal ECDF (black) vs Normal CDF (blue)",
        remp = function(x)stats::rnorm(x),
        ptrue = function(x)stats::pnorm(x))
```

